Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
5% additional sentence + minor change

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] 
In 
`r sum(project_plan$power_standard == "80% power")`
cases, we powered the replication attempt to 80\% post-hoc power. In 
`r sum(project_plan$power_standard == "Original")` 
cases, we used the original sample size. Three replications deviated from these two criteria.  In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.  In another, we reduced the number of trials as part of the adaptation to Mechanical Turk. In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage (details available in SOM).

@@

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Our three-point rating system was based on the theoretical interpretation of the original finding, with 0\% = no support for the original interpretation, 50\% = some support for the original interpretation, 100\% = full replication). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r 100 * round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)`\% and `r 100 * round(mean(d$replicated_student, na.rm=TRUE), digits = 2)`\% respectively.

>>>>

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget. For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved desired power if some participants skipped through or did not complete the experiment.
^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] 
In 
`r sum(project_plan$power_standard == "80% power")`
cases, we powered the replication attempt to 80\% post-hoc power. In 
`r sum(project_plan$power_standard == "Original")` 
cases, we used the original sample size. Three replications deviated from these two criteria.  In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.  In another, we reduced the number of trials as part of the adaptation to Mechanical Turk. In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage (details available in SOM).

@@

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Our three-point rating system was based on the theoretical support for the original finding, "None" (no support; 0\%), "Partial" (some support; 50\%), and "Full" (replication consistent with original interpretation; 100\%). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r 100 * round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)`\% and `r 100 * round(mean(d$replicated_student, na.rm=TRUE), digits = 2)`\% respectively.
